%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Ahmed Khafaji} \\ \vspace{1pt}
    Toronto, Canada \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 647-765-6229 ~ 
    \href{mailto:ahmedkhafaji11@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{ahmedkhafaji11@gmail.com}} ~ 
    \href{https://linkedin.com/in/ahmed-khafaji}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/ahmed-khafaji}}  ~
    \href{https://github.com/khafaji-ahmed}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/khafaji-ahmed}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {York University}{Sep. 2020 -- Apr. 2025}
      {Bachelor of Engineering in Software Engineering}{Toronto, ON, Canada}
      % \resumeItemListStart
      %   \resumeItem{GPA: 7.4/9}
      % \resumeItemListEnd
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    \begin{multicols}{4}
        \begin{itemize}[itemsep=-5pt, parsep=3pt]
            \item\small Data Structures
            \item Software Methodology
            \item Algorithms Analysis
            \item Database Management
            \item Artificial Intelligence
            \item Internet Technology
            \item Systems Programming
            \item Computer Architecture
        \end{itemize}
    \end{multicols}
    
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {CAYDE SERVICES INC.}{2022 -- Present}
      {Founder \& Lead Engineer}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Bootstrapped and led a Canadian software company delivering government and campus-scale solutions.}
        \resumeItem{Built and scaled yuMeet, a university social platform with real-time messaging and event matchmaking.}
        \resumeItem{Oversaw technical architecture, hiring, partnerships, and go-to-market strategy across projects.}
      \resumeItemListEnd

      \resumeSubheading
      {Distinctive Wood Products}{Feb. 2024 -- Present}
      {Full-Stack Software Engineer}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Sole developer responsible for modernizing and maintaining internal business systems using PHP, JavaScript, and SQL in a legacy environment.}
        \resumeItem{Redesigned critical backend workflows and database schemas, reducing system lag and query times by over 30\%.}
        \resumeItem{Improved internal operations by building custom tools for order tracking, invoicing, and production, tailored to non-technical staff needs.}
      \resumeItemListEnd
    

    \resumeSubheading
      {Lightring AI}{Nov. 2022 -- Present}
      {Senior Full-Stack Developer \& Team Lead}{Toronto, Canada}
      \resumeItemListStart
        \resumeItem{Directed the development of critical projects for government and healthcare sectors, increasing client retention by 15\%.}
        \resumeItem{Introduced CI/CD pipelines and DevOps practices, reducing deployment times by 50\%.}
        \resumeItem{Mentored junior developers and conducted code reviews, improving team communication and productivity.}
        \resumeItem{Led multi-platform app development that boosted workflow efficiency by 25\% across the organization.}
        \resumeItem{Collaborated with stakeholders to define technical requirements and project roadmaps.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{yuMeet -- Campus Social App} $|$ \emph{React Native, Next.js, PostgreSQL, Socket.IO}}{2025}
          \resumeItemListStart
            \resumeItem{Led development of a scalable matchmaking and messaging platform for York University students, supporting 55k+ users.}
            \resumeItem{Architected client-server model with real-time messaging, user verification, event creation, and personalized recommendations.}
            \resumeItem{Designed a performance-first infrastructure to support concurrent usage with offline fallback and local-first data sync.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Enterprise Billing System} $|$ \emph{Next.js, Node.js, PostgreSQL}}{2024}
          \resumeItemListStart
            \resumeItem{Architected and developed a scalable billing system for the Iraq government, processing over 100k daily transactions.}
            \resumeItem{Integrated multiple payment gateways and implemented real-time transaction monitoring for enhanced scalability.}
            \resumeItem{Designed microservices architecture with load balancing, ensuring 99.9\% uptime and fault tolerance.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Government E-Visa Platform} $|$ \emph{Next.js, React, MongoDB}}{2023}
          \resumeItemListStart
            \resumeItem{Built comprehensive visa application system for Iraq ministry, reducing application processing time by 40\%.}
            \resumeItem{Created dynamic content management admin system, engaging 50k+ monthly users with improved UX.}
            \resumeItem{Implemented advanced security features including document verification and fraud detection algorithms.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, C, HTML/CSS, JavaScript, TypeScript, PHP, SQL} \\
     \textbf{Developer Tools}{: VS Code, Google Cloud Platform, Eclipse, Jenkins, GitHub, Docker, Kubernetes} \\
     \textbf{Technologies/Frameworks}{: React, Next.js, Node.js, Express, Linux, Docker, Virtual Machines, Third-party APIs} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, Redis, MySQL} \\
     \textbf{Leadership \& Achievements}{: Team leadership, code architecture, performance optimization, technical mentoring, DevOps implementation} \\
    }}
 \end{itemize}
 \vspace{-16pt}

\end{document}